### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@3e666f58ad67a514231fb4cb5f195ef5d3a55b80 🚀

\begin{longtable}[]{@{}llll@{}}
\toprule
Method & Embedding approach & Reference & Ecological
application\tabularnewline
\midrule
\endhead
RDPG & graphs through SVD & Young \& Scheinerman (2007) & Wardeh et al.
(2021)\tabularnewline
tSNE & nodes through statistical divergence & Hinton \& Roweis (2002)
&\tabularnewline
DeepWalk & graph walk & Perozzi et al. (2014) &\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow (2015)
&\tabularnewline
LINE & nodes through statistical divergence & Tang et al. (2015)
&\tabularnewline
SDNE & nodes through auto-encoding & D. Wang et al. (2016)
&\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016) &\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)
&\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)
&\tabularnewline
Joint methods & multiple graphs & S. Wang et al. (2021) &\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

>>>>

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.10\columnwidth}\raggedright
Method\strut
\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedright
Embedding approach\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
Reference\strut
\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
Species interactions application\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.10\columnwidth}\raggedright
RDPG\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
graphs through SVD\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Young \& Scheinerman (2007)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
Poisot et al. (2021)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
tSNE\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
nodes through statistical divergence\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Hinton \& Roweis (2002)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
Cieslak et al. (2020) -- statistical interactions\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
DeepWalk\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
graph walk\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Perozzi et al. (2014)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
Wardeh et al. (2021)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
FastEmbed\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
graph through PCA/SVD analogue\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Ramasamy \& Madhow (2015)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
LINE\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
nodes through statistical divergence\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Tang et al. (2015)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
SDNE\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
nodes through auto-encoding\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
D. Wang et al. (2016)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
node2vec\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
node embedding\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Grover \& Leskovec (2016)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
graph2vec\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
sub-graph embedding\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
Narayanan et al. (2017)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
DMSE\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
joint node embedding\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
D. Chen et al. (2017)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
D. Chen et al. (2017) -- joint SDMs\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
HARP\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
nodes through a meta-strategy\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
H. Chen et al. (2017)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright
Joint methods\strut
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedright
multiple graphs\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
S. Wang et al. (2021)\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Chen2017DeeMul}{}%
Chen, D., Xue, Y., Fink, D., Chen, S., \& Gomes, C. P. (2017).
\emph{Deep Multi-species Embedding}. 3639--3646.
\url{https://www.ijcai.org/proceedings/2017/509}

@@

\leavevmode\hypertarget{ref-Cieslak2020TdiSto}{}%
Cieslak, M. C., Castelfranco, A. M., Roncalli, V., Lenz, P. H., \&
Hartline, D. K. (2020). T-Distributed Stochastic Neighbor Embedding
(t-SNE): A tool for eco-physiological transcriptomic analysis.
\emph{Marine Genomics}, \emph{51}, 100723.
\url{https://doi.org/10.1016/j.margen.2019.100723}

@@

\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J. (2021,
May 31). \emph{Imputing the mammalian virome with linear filtering and
singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
